BEX3012 Project Analysis

### 2017-04-24 Internship/BEX3012ProjectReport.Rmd
Report cache change
Additions to BEXreport
structure, processing sections

```{r cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE)

library(tidyverse)
library(readr)
library(GGally)

@@

EmotionSoftwareSpecs <- read_csv("Figures/EmotionSoftwareSpecifications.csv")

#Create normalised SB values
SB <- SB %>%
  rowwise %>% mutate(z = (anger.confidence+
               disgust.confidence+
               fear.confidence+
               happiness.confidence+
               neutral_mood.confidence+
               sadness.confidence+
               surprise.confidence)) %>%
  mutate(anger = anger.confidence/z,
         disgust = disgust.confidence/z,
         fear = fear.confidence/z,
         happiness = happiness.confidence/z,
         neutral = neutral_mood.confidence/z,
         sadness = sadness.confidence/z,
         surprise = surprise.confidence/z)

```{r}
#Create normalised GE values
Conf <- function(Emot){
ifelse(Emot=="VERY_UNLIKELY", 10,  
        ifelse(Emot == "UNLIKELY", 30, 
                ifelse(Emot == "POSSIBLE", 50, 
                ifelse(Emot == "LIKELY", 70, 
                ifelse(Emot == "VERY_LIKELY", 90, NA)))))
}

GE <- GE %>% mutate(joyConf = Conf(joyLikelihood)) %>%
  mutate(sorrowConf = Conf(sorrowLikelihood)) %>%
  mutate(angerConf = Conf(angerLikelihood)) %>%
  mutate(surpriseConf = Conf(surpriseLikelihood))

GE <- GE %>%
  rowwise %>% 
  mutate(neutralConf = 100 - (pmax(joyConf, sorrowConf, angerConf, surpriseConf))) %>%
  mutate(z = (joyConf+
                sorrowConf+
                angerConf+
                surpriseConf+
                neutralConf)) %>%
  mutate(anger = angerConf/z,
         joy = joyConf/z,
         neutral = neutralConf/z,
         sorrow = sorrowConf/z,
         surprise = surpriseConf/z)

# Introduction

@@

# Method

## Materials

### Pre Processing Images

A subset of faces was created specifically for emotion recognition purposes. To present only a single face to each software required cropping the region of the image based on Google’s bounding box result^[coordinates derived from prior study].
Each new image created contained the area within the face bounding boxes found in the previous study, as well as a small border to frame the face. This resulted in images of differing sizes to be passed to the APIs. These 1319 new images were hosted on Google Drive to allow for URL access from the API to the individual images.

@@

library(magick)
library(grid)
library(gridExtra)
library(ggplot2)

@@

  t <- tableGrob(dl, theme = ttheme_minimal(), rows = c("", "", ""))

@@

### Software APIs

We have considered three Emotion Recognition APIS.
They were chosen for their accessibility and online reviews, as these are well recognised options for Facial recongition currently available.

The number of emotions shown in the results were not congruent. These differences required pre processing to find the most comparable results for analysis.
Microsoft provided the most emotion options, contempt being the addition that was not provided by Skybiometry. Google provided the least, only giving the options for four different emotions.

### Processing API results

As the results provided by each of the software differed, processing was needed to create comparable sets.

#### Microsoft

@@

knitr::kable(MEexample[2:9], digits=6, longtable=TRUE, booktabs = TRUE, caption="The Microsoft API provided 8 numerical values, one for each emotion.")
```

#### Skybiometry

```{r SBexample, echo=F, fig.cap = "\\label{tab:SBexample}"}
SBexample <- SB %>% subset(aname=="face-1745-1-Go.png") %>% select(ends_with(".confidence"))

knitr::kable(SBexample[3:9], digits=6, longtable=TRUE, booktabs = TRUE,
             col.names = c("neutral", "anger", "disgust", "fear",
                           "happiness", "sadness", "surprise"),
             caption="The Skybiometry API provided 7 numerical Confidence values, one for each emotion.")
```

#### Google

@@

These differing outputs needed to be arranged in a comparable manner.
We began by considering the Microsoft output. Noticing that the sums of all emotion values was approximately one we considered that dividing the individual Skybiometry emotion confidences by the sum of the confidences would give the likelihood of each emotion being the dominant emotion in a face.

@@

We then needed to transform the Google output to also be comparable. This was the most challenging due to it's unusual form.

A numeric value was assigned to each possible likelihood value. This would allow for numeric comparisons to be made.
The values were assigned according to the table below:

@@

knitr::kable(LT, longtable=TRUE, booktabs = TRUE,
               caption="")

@@

As both Microsoft and Skybiometry included a neutral category we considered how we may incorporate this for the Google results.

Google Transformed

Our approach considered that when a face was "very unlikely" to be any of the four emotion categories it could be deemed "neutral". However when one emotion was stronger than other it could still be possible that the face only had a small lean toward this emotion. Therefore the Confidence value for neutral was derived as:

The process to derive the numeric values followed the process undertaken for Skybiometry values. Where the individual emotion confidences were divided by the sum of the emotion confidence values for each face.

This resulted in congruent emotion data to be compared

GET <- GE %>% subset(FileName=="face-1745-1-Go.png") %>% 
  select(joy, sorrow, anger, surprise, neutral)

# Analysis
# Validation
We considered a subset of images where the emotions on the faces were manually considered.

>>>>

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE, fig.width = 8)

library(tidyverse)
library(dplyr)
library(readr)
library(GGally)
library(magick)
library(grid)
library(gridExtra)
library(ggplot2)

@@

EmotionSoftwareSpecs <- read_csv("Figures/EmotionSoftwareSpecifications.csv")
```

```{r normalise, cache=FALSE}
#Create normalised SB values
SB <- SB %>%
  rowwise %>% mutate(z = (anger.confidence+
               disgust.confidence+
               fear.confidence+
               happiness.confidence+
               neutral_mood.confidence+
               sadness.confidence+
               surprise.confidence)) %>%
  mutate(anger = anger.confidence/z,
         disgust = disgust.confidence/z,
         fear = fear.confidence/z,
         happiness = happiness.confidence/z,
         neutral = neutral_mood.confidence/z,
         sadness = sadness.confidence/z,
         surprise = surprise.confidence/z)

#Create normalised GE values
Conf <- function(Emot){
ifelse(Emot=="VERY_UNLIKELY", 10,  
        ifelse(Emot == "UNLIKELY", 30, 
                ifelse(Emot == "POSSIBLE", 50, 
                ifelse(Emot == "LIKELY", 70, 
                ifelse(Emot == "VERY_LIKELY", 90, NA)))))
}
```

```{r mutate}
#confidence columns
GE <- GE %>% mutate(joyConf = Conf(joyLikelihood)) %>%
  mutate(sorrowConf = Conf(sorrowLikelihood)) %>%
  mutate(angerConf = Conf(angerLikelihood)) %>%
  mutate(surpriseConf = Conf(surpriseLikelihood))

#proportion columns
GE <- GE %>%
  rowwise %>% 
  mutate(neutralConf = 100 - (pmax(joyConf, sorrowConf, angerConf, surpriseConf))) %>%
  mutate(z = (joyConf+
                sorrowConf+
                angerConf+
                surpriseConf+
                neutralConf)) %>%
  mutate(anger = angerConf/z,
         joy = joyConf/z,
         neutral = neutralConf/z,
         sorrow = sorrowConf/z,
         surprise = surpriseConf/z)

#player name column
GE <- GE %>% rowwise %>%
  mutate(playerName = ifelse(PlayerNumber == 1, player1,
                                            ifelse(PlayerNumber == 2, player2,
                                                   ifelse(is.na(PlayerNumber), NA, NA))))
```

```{r playerSubset}
GEP <- GE %>% filter(detect == "Player")
MEP <- ME %>% filter(detect == "Player")
SBP <- SB %>% filter(detect == "Player")
```

\newpage
# Introduction

@@

# Materials

## Images

The image set contained 6406 still shot 800x450px size video frames, taken every 3 seconds from 5 minute segments sampled from 105 Australian Open 2016 match broadcast videos.
The broadcast videos are a combination of multiple camera feeds, these angles vary depending on the court the match was played on.

```{r ExampleImage, echo=F, fig.cap = "Example Image: 2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0020.png\\label{fig:ExampleImage}"}

img <- image_read("Figures/2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0020.png")

p <- ggplot() + theme_void() + annotation_custom(rasterGrob(img)) +
      coord_cartesian(xlim=c(0, 800), ylim=c(0,450))
p
```

## Software APIs

Three emotion recognition APIS were considered.
They were chosen for their accessibility and online reviews of their performance, and these are well recognised options for Facial recognition currently available.

The number of emotions shown in the results were not congruent. These differences made it necessary to pre process the result to provide the most comparable results for analysis.
Microsoft provided the most emotion options, contempt being the addition that was not provided by Skybiometry. Google provided the least, only giving the options for four different emotions.

\newpage
# Procedure

## Process Images

The original image set was subset to create images of faces specifically suited for emotion recognition purposes. 
A crop was performed to create a new image that focused on the area marked as a face by Google^[based on Google’s bounding box coordinates]. A border to frame the face was also included for visual appeal.
These 1319 new images, of varying sizes, were hosted on Google Drive to allow for URL access from the API to the individual images.

@@

@@

  t <- tableGrob(dl, theme = ttheme_minimal(core=list(fg_params=list(hjust=0, x=0.1)),
                      rowhead=list(fg_params=list(hjust=0, x=0))), rows = c("", "", ""))

@@

## Process API results

The results extracted from each of the APIs differed, re configuring of these results was needed to create comparable sets for analysis.

Microsoft provided a POST request object in a JSON format. 
This was easily formatted to create a data set of the eight numeric emotion values provided for each face. In the event that emotion values were not returned for a certain face, NAs were presented in the data set.

@@

knitr::kable(MEexample[2:9], digits=6, longtable=TRUE, booktabs = TRUE, caption="The Microsoft API provided eight numerical values, one for each emotion.")
```

Skybiometry as provided a POST request object in a JSON format. However, unlike Microsoft, the results included a True or False Value for each of the seven emotions and a confidence level   'confidence value as a percentage from 0 to 100'^[https://skybiometry.com/documentation/#document-21] representing the confidence of the emotion being present on a player's face.

```{r SBexample, echo=F, fig.cap = "\\label{tab:SBexample}"}

SBexample <- SB %>% subset(aname=="face-1745-1-Go.png") %>% select(ends_with(".confidence"))

knitr::kable(SBexample[3:9], digits=6, longtable=TRUE, booktabs = TRUE,
             col.names = c("neutral", "anger", "disgust", "fear",
                           "happiness", "sadness", "surprise"),
             caption="The Skybiometry API provided seven numerical Confidence values, one for each emotion.")
```

The process undertaken to receive results Google produces was the same as the previous APIs. However rather than numeric values, it returned categorical likelihoods for the four emotions it considered.

@@

These differing outputs needed to be arranged in a comparable manner.
Noticing that the sums of the individual emotions for each face in the Microsoft results was approximately one provided the basis for transformation for the other APIs. Dividing the individual Skybiometry emotion confidences by the sum of the confidences would give the proportional likelihood of each emotion being the dominant emotion in a face.

@@

Google's results then required a more complex transformation for the output to also be comparable.

As there were five possible categories assigned to each emotion the numeric values were chosen to sit in the middle of five 20 point ranges. This allowed a numerical representation of each possible likelihood value and would allow for numeric comparisons to be made.
The values were assigned according to the table below:

@@

knitr::kable(LT, longtable=TRUE, booktabs = TRUE, caption="")
```

As both Microsoft and Skybiometry included a neutral category we considered how to incorporate a neutral category for the Google results.

Our approach considered that when a face was "very unlikely" to be any of the four emotion categories it could be deemed "neutral". However when one emotion was stronger than other it could still be possible that the face only had a small lean toward this emotion and it may not be the obvious choice. Therefore the Confidence value for neutral was calculated according to the formula below:

The process to derive the numeric values for Google followed the process undertaken for Skybiometry values. Where the individual emotion confidences were divided by the sum of the emotion confidence values for each face. This resulted in congruent emotion data.

GET <- GEP %>% subset(FileName=="face-1745-1-Go.png") %>% 
  select(joy, sorrow, anger, surprise, neutral)

\newpage
# Analysis

Each API returned a different amount of non null results. Microsoft produced emotion results for `r sum(!is.na(ME$anger))` faces. This was more than Skybiometry, as it produced only `r sum(!is.na(SB$anger))` results for emotions on faces. Google provided the most, with  `r sum(!is.na(GE$anger))` emotion results^[As the initial set was faces identified by Google there is the possibility of bias toward being able to identify emotions in faces it was able to find originally.].

```{r GEPhists}
gganG <- ggplot(GEP, aes(x=anger))+geom_histogram(binwidth=0.055)+
  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
ggjoG <- ggplot(GEP, aes(x=joy))+geom_histogram(binwidth=0.055) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
ggneG <- ggplot(GEP, aes(x=neutral))+geom_histogram(binwidth=0.055) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
ggsoG <- ggplot(GEP, aes(x=sorrow))+geom_histogram(binwidth=0.055) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
ggsuG <- ggplot(GEP, aes(x=surprise))+geom_histogram(binwidth=0.055) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))

grid.arrange(gganG,ggjoG,ggneG,ggsoG,ggsuG,nrow=2,
             top=textGrob("Google Distribution of Emotion Porportions",gp=gpar(fontsize=20,font=3)))

@@

```{r SBPhists}
gganS <- ggplot(SBP, aes(x=anger))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
gghaS <- ggplot(SBP, aes(x=happiness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
ggneS <- ggplot(SBP, aes(x=neutral))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
ggsaS <- ggplot(SBP, aes(x=sadness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
ggsuS <- ggplot(SBP, aes(x=surprise))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
ggdiS <- ggplot(SBP, aes(x=disgust))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
ggfeS <- ggplot(SBP, aes(x=fear))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))

grid.arrange(gganS, gghaS, ggneS, ggsaS, ggsuS, ggdiS, ggfeS,nrow=3,
             top=textGrob("Skybiometryh Distribution of Emotion Porportions",gp=gpar(fontsize=20,font=3)))

```{r MEPhists}
gganM <- ggplot(MEP, aes(x=anger))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
gghaM <- ggplot(MEP, aes(x=happiness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
ggneM <- ggplot(MEP, aes(x=neutral))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
ggsaM <- ggplot(MEP, aes(x=sadness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
ggsuM <- ggplot(MEP, aes(x=surprise))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
ggdiM <- ggplot(MEP, aes(x=disgust))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
ggfeM <- ggplot(MEP, aes(x=fear))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
ggcoM <- ggplot(MEP, aes(x=contempt))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))

grid.arrange(gganM, gghaM, ggneM, ggsaM, ggsuM, ggdiM, ggfeM, ggcoM,nrow=3, 
             top=textGrob("Microsoft Distribution of Emotion Porportions",gp=gpar(fontsize=20,font=3)))

\newpage
# Validation
We considered a subset of images where the emotions on the faces were manually considered.

### 2017-04-24 Internship/EmotionsAnalysis.Rmd
Additions to BEXreport
structure, processing sections

```{r SBhists}

ggSBPne <- ggplot(SBP, aes(x=neutral))+geom_histogram(binwidth=0.025) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggSBPan <- ggplot(SBP, aes(x=anger))+geom_histogram(binwidth=0.025) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggSBPdi <- ggplot(SBP, aes(x=disgust))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggSBPfe <- ggplot(SBP, aes(x=fear))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggSBPha <- ggplot(SBP, aes(x=happiness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggSBPsa <- ggplot(SBP, aes(x=sadness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggSBPsu <- ggplot(SBP, aes(x=surprise))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))

grid.arrange(ggSBPne,
             ggSBPan,
             ggSBPdi,
             ggSBPfe,
             ggSBPha,
             ggSBPsa,
             ggSBPsu, nrow=3)
```

SBPCL: Long form of Confidence levels of SB results
```{r}
SBPCL <- SBP %>% group_by(aname) %>% 
  gather(key = Emotion, value=EmotionValue, anger,disgust,fear,happiness,neutral,sadness,surprise)

@@

GEP: Long form of Confidence levels of GE results
GEPN:  Long form of Confidence levels of GE results renamed to match
```{r}
#rename
GEPN <- GEP %>% select(FileName, anger, happiness=joy, sadness=sorrow, surprise, neutral, everything())

@@

Microsoft Emotion plots
```{r}
ggMEPne<-ggplot(MEP, aes(x=neutral)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPan<-ggplot(MEP, aes(x=anger)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPdi<-ggplot(MEP, aes(x=disgust)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPfe<-ggplot(MEP, aes(x=fear)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPha<-ggplot(MEP, aes(x=happiness)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPsa<-ggplot(MEP, aes(x=sadness)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPsu<-ggplot(MEP, aes(x=surprise)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))

grid.arrange(ggMEPne,
             ggMEPan,
             ggMEPdi,
             ggMEPfe,
             ggMEPha,
             ggMEPsa,
             ggMEPsu, nrow=3)

@@

Microsoft Long form 
MEPCL: Long form of Confidence levels of ME results
```{r}
MEPCL<-MEP %>% group_by(FileName) %>% 
  gather(key = Emotion, value=EmotionValue, anger,contempt,disgust,fear,happiness,neutral,sadness,surprise)

@@

###
Join emotions for each face
J2: Table of FileNames and associated dominant emotion
```{r}
S1 <- select(SBPCL1, FileName = aname , SEmotion = Emotion)
S2 <- select(MEPCL1, FileName, MEmotion = Emotion)
S3 <- select(GEPCL1, FileName, GEmotion = Emotion)
J1 <- full_join(S1, S2, by = "FileName")
J2 <- full_join(J1, S3, by = "FileName")

@@

```{r}
set.seed(300)
J2na<-na.omit(J2)
FL<-sample(J2na$FileName, 50)
J2na<-J2na %>% subset(FileName %in% FL)

@@

Find images from matches played by certain players
```{r}
a <- as.data.frame(table(GEP$player1))
a <- a %>% arrange(-Freq)

@@

subset of Google where neutral = another category
```{r}
neutrals <- GEPCL1 %>% filter(neutralConf==joyConf | 
                    neutralConf==sorrowConf | 
                    neutralConf==surpriseConf | 
                    neutralConf==angerConf) %>%
  filter(neutralConf != 10)

@@

Emotive Player Faces
EF: Emotive Player Faces to be used as sample.
It is hard to classify many of the faces as one of the seven possible options. Where hints of emotive expressions can be attributed to one or more faces
```{r}

@@

Player Emotion Tables
Distribution of emotion values for particular emotions across all images of a player
```{r Playerhists}
ggplot(na.omit(SBP), aes(x=playerName))+geom_bar()+ theme(axis.text.x = element_text(angle = 20))

@@

@@

  ggSBPan <- 
    ggplot(SBPplayer, aes(x = anger)) + ggtitle("Skybiometry") +
    geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))

  GEPplayer <- GEP %>% filter(playerName == Name)

  ggGEPan <-
    ggplot(GEPplayer, aes(x = anger)) +  ggtitle("Google") +
    geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))

@@

  ggMEPan <-
    ggplot(MEPplayer, aes(x = anger)) +  ggtitle("Microsoft") +
    geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))

grid.arrange(ggMEPan,ggSBPan,ggGEPan, nrow = 3)

TB<- as.list(MEPplayer$FileName)
DisplayFaces(TB)
```

>>>>

```{r SBhists}
plotSBHists<-function(data) {
ggne <- ggplot(data, aes(x=neutral))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggan <- ggplot(data, aes(x=anger))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggdi <- ggplot(data, aes(x=disgust))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggfe <- ggplot(data, aes(x=fear))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggha <- ggplot(data, aes(x=happiness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggsa <- ggplot(data, aes(x=sadness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggsu <- ggplot(data, aes(x=surprise))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))

grid.arrange(ggne,ggan,ggdi,ggfe,ggha,ggsa,ggsu,nrow=3)
}

plotEmotion<-function(data, Emotion) {
ggEmot <- ggplot(data, aes_string(x=Emotion))+geom_histogram(binwidth=0.025) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
}

SBPCL: Long form of Confidence levels of SB results
```{r SBPlong}
SBPCL <- SBP %>% group_by(aname) %>% 
  gather(key = Emotion, value=EmotionValue, anger,disgust,fear,happiness,neutral,sadness,surprise)

@@

GEP: Long form of Confidence levels of GE results
GEPN:  Long form of Confidence levels of GE results renamed to match
```{r GEPlong}
#rename
GEPN <- GEP %>% select(FileName, anger, happiness=joy, sadness=sorrow, surprise, neutral, everything())

@@

Microsoft Emotion plots
```{r MEhists}
plotMEHists<-function(data) {
ggMEPne<-ggplot(MEP, aes(x=neutral)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPan<-ggplot(MEP, aes(x=anger)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPdi<-ggplot(MEP, aes(x=disgust)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPfe<-ggplot(MEP, aes(x=fear)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPha<-ggplot(MEP, aes(x=happiness)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPsa<-ggplot(MEP, aes(x=sadness)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPsu<-ggplot(MEP, aes(x=surprise)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPco<-ggplot(MEP, aes(x=contempt)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))

grid.arrange(ggMEPne,
             ggMEPan,
             ggMEPdi,
             ggMEPfe,
             ggMEPha,
             ggMEPsa,
             ggMEPsu, 
             ggMEPco,nrow=3)
}

@@

Microsoft Long form 
MEPCL: Long form of Confidence levels of ME results
```{r MElong}
MEPCL<-MEP %>% group_by(FileName) %>% 
  gather(key = Emotion, value=EmotionValue, anger,contempt,disgust,fear,happiness,neutral,sadness,surprise)

@@

###
Join emotions for each face
J2: Table of FileNames and associated dominant emotion
```{r combined}
S1 <- select(SBPCL1, FileName = aname , SEmotion = Emotion)
S2 <- select(MEPCL1, FileName, MEmotion = Emotion)
S3 <- select(GEPCL1, FileName, GEmotion = Emotion)
J1 <- full_join(S1, S2, by = "FileName")
J2 <- full_join(J1, S3, by = "FileName")

@@

```{r table}
set.seed(300)
J2na<-na.omit(J2)
FL<-sample(J2na$FileName, 50)
J2na<-J2na %>% subset(FileName %in% FL)

@@

Find images from matches played by certain players
```{r playerMatches}
a <- as.data.frame(table(GEP$player1))
a <- a %>% arrange(-Freq)

@@

subset of Google where neutral = another category
```{r GoogleNeutral}
neutrals <- GEPCL1 %>% filter(neutralConf==joyConf | 
                    neutralConf==sorrowConf | 
                    neutralConf==surpriseConf | 
                    neutralConf==angerConf) %>%
  filter(neutralConf != 10)

@@

Emotive Player Faces
EF: Emotive Player Faces to be used as sample.
It is hard to classify many of the faces as one of the seven possible options. Where hints of emotive expressions can be attributed to one or more faces
```{r EmotiveFaces}

@@

Player Emotion Tables
Distribution of emotion values for particular emotions across all images of a player
```{r PlayerHists}
ggplot(na.omit(SBP), aes(x=playerName))+geom_bar()+ theme(axis.text.x = element_text(angle = 20))

@@

EmotionHists <- function(Emotion, Name){

@@

  ggSBPan <- 
    ggplot(SBPplayer, aes_string(x = Emotion)) + ggtitle("Skybiometry") +
    geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))

  GEPplayer <- GEPN %>% filter(playerName == Name)

  ggGEPan <-
    ggplot(GEPplayer, aes_string(x = Emotion)) +  ggtitle("Google") +
    geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))

@@

  ggMEPan <-
    ggplot(MEPplayer, aes_string(x = Emotion)) +  ggtitle("Microsoft") +
    geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))

grid.arrange(ggMEPan,ggSBPan,ggGEPan, nrow = 3) 
}

EmotionHists(Emotion = "anger", "GSimon")
EmotionHists(Emotion = "surprise", "GSimon")
EmotionHists(Emotion = "happiness", "GSimon")
EmotionHists(Emotion = "sadness", "GSimon")

Neutrality in Faces
```{r}
sum(MEPCL1$Emotion=="neutral")/nrow(MEPCL1)
sum(SBPCL1$Emotion=="neutral")/nrow(SBPCL1)
sum(GEPCL1$Emotion=="neutral")/nrow(GEPCL1)

nrow(MEPCL1)-sum(MEPCL1$Emotion=="neutral")
nrow(SBPCL1)-sum(SBPCL1$Emotion=="neutral")
nrow(GEPCL1)-sum(GEPCL1$Emotion=="neutral")

Pairwise comparison of neutral overlaps
```{r neutrality}
J2ne<-J2 %>% rowwise() %>%
  mutate(SEneutral = ifelse(SEmotion=="neutral", "neutral","non-neutral")) %>%
  mutate(MEneutral = ifelse(MEmotion=="neutral", "neutral","non-neutral")) %>%
  mutate(GEneutral = ifelse(GEmotion=="neutral", "neutral","non-neutral"))

S4 <- select(SBP, FileName = aname, Skybiometry = neutral)
S5 <- select(MEP, FileName, Microsoft = neutral)
S6 <- select(GEP, FileName, Google = neutral)
J3 <- full_join(S4, S5, by = "FileName")
J4 <- full_join(J3, S6, by = "FileName")

J4 <- J4 %>% rowwise %>% mutate(GoogleJitter = jitter(Google))

library(GGally)
ggscatmat(as.data.frame(na.omit(J4[,c(2:3,5)])))

table(J2ne$MEmotion, J2$GEmotion)
table(J2ne$MEneutral, J2ne$GEneutral)
```

Bar chart of attributes for neutral categorisations
Need to consider that higher levels of values across the population may create misleading plots.

```{r}
Gneutral <- GEPCL1 %>% filter(Emotion=="neutral")
Mneutral <- MEPCL1 %>% filter(Emotion=="neutral")
Sneutral <- SBPCL1 %>% filter(Emotion=="neutral")

NeutralBars <- function(Attribute){

  ggSBPne <- 
    ggplot(Sneutral, aes_string(x = Attribute)) + ggtitle("Skybiometry") +
    geom_bar()

  ggGEPne <-
    ggplot(Gneutral, aes_string(x = Attribute)) + ggtitle("Google") +
    geom_bar()

  ggMEPne <-
    ggplot(Mneutral, aes_string(x = Attribute)) + ggtitle("Microsoft") +
    geom_bar()

grid.arrange(ggMEPne,ggSBPne,ggGEPne, nrow = 3) 
}

NeutralBars(Attribute = "bg")
```
